6.830 Project Proposal \\ \large Data Imputation as a Query Optimization

### 2016-10-12 main.tex
Add milestones.

\section{Project Milestones}
\end{document}

>>>>

\section{Project Milestones}

We outline a series of milestones to be completed:
\begin{enumerate}
\item Initial data collection and query workload for evaluation.
\item Consolidate set of imputation strategies.
\item Formalize a measure of uncertainty, completeness and cost in imputation as related to 2.
\item Formalize the possible query rewrites when using an imputation operator.
\item Incorporate imputation-related measures into cost estimation for SimpleDB.
\item Incorporate imputation-related rewrites for SimpleDB.
\item Evaluate performance.
\end{enumerate}
\end{document}
